---
title: "Usage of 'wrappedtools'"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Usage of wrappedtools}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(wrappedtools)
```

# 'wrappedtools'

<!-- badges: start -->
<!-- badges: end -->

The goal of 'wrappedtools' is to make my (and possibly your) life a bit easier 
by a set of convenience functions for many common tasks like e.g. computation
of mean and SD and pasting them with ±. Instead of   
paste(round(mean(x),some_level), round(sd(x),some_level), sep='±')  
a simple meansd(x, roundDig = some_level) is enough.   


## Installation

You can install the released version of 'wrappedtools' from github with:

``` r
devtools::install_github("abusjahn/wrappedtools")
```
```{r include=FALSE}
library(wrappedtools)
```

## Examples

This is a basic example which shows you how to solve a common problem,
that is, describe and test differences in some measures between 2 samples,
rounding descriptive statistics to a reasonable precision in the process:   

```{r example1}
# Standard functions to obtain median and quartiles:
median(mtcars$mpg)
quantile(mtcars$mpg,probs = c(.25,.75))
# wrappedtools adds rounding and pasting:
median_quart(mtcars$mpg)
# on a higher level, this logic leads to
compare2numvars(data = mtcars, dep_vars = c('wt','mpg', "disp"), 
                indep_var = 'am',
                gaussian = F,
                round_desc = 3)
```

To explain the *wrapper' part of the package name, here is another example, 
using the ks.test as test for a Normal distribution, where ksnormal simply
wrapps around the ks.test function:   
```{r example2}
somedata <- rnorm(100)
ks.test(x = somedata, 'pnorm', mean=mean(somedata), sd=sd(somedata))

ksnormal(somedata)
```
This should give you the general idea, I'll try to expand this intro over time...
